---
title: "A Step-By-Step Guide To Web Scraping With R"
format: html
editor: visual
---

[Dario Radecic](A%20Step-By-Step%20Guide%20To%20Web%20Scraping%20With%20R%20%7C%20Better%20Data%20Science)

## **Plan of attack**

The goal to grab the information for every book in a category:

-   Title: h3\>a\>title property

-   Rating: p.star-rating \> class attribute

-   Price: div.product_price \> div.price_color \> text

-   Availability: div.product_price \> div.instock \> text

-   Book URL: div.image_container \> a \> href \> property

## Libraries

```{r}
pacman::p_load(tidyverse, rvest)
```

## Scrapping

```{r}
url <- 'http://books.toscrape.com/catalogue/category/books/travel_2/index.html'
```

Getting information sections: title, url, image, rating, price, availability:

```{r}
titles <- read_html(url) |>
  html_nodes('h3') %>%
  html_nodes('a') |>
  html_text()
```

```{r}
urls <- read_html(url) %>%
  html_nodes('.image_container') |>
  html_nodes('a') |>
  html_attr('href') |>
  str_replace_all('../../../', '/')
```

```{r}
imgs <- read_html(url) %>% 
  html_nodes('.image_container') %>%
  html_nodes('img') %>%
  html_attr('src') %>%
  str_replace_all('../../../../', '/')
```

```{r}
ratings <- read_html(url) %>% 
  html_nodes('p.star-rating') %>% 
  html_attr('class') %>% 
  str_replace_all('star-rating ', '')
```

```{r}
prices <- read_html(url) %>% 
  html_nodes('.product_price') %>% 
  html_nodes('.price_color') %>% 
  html_text()
```

```{r}
availability <- read_html(url) %>% 
  html_nodes('.product_price') %>% 
  html_nodes('.instock') %>% 
  html_text() %>% 
  str_trim()
```

Grouping all sections into a single dataframe:

```{r}
scraped <- data.frame(
  Title = titles, 
  URL = urls, 
  SourceImage = imgs, 
  Rating = ratings, 
  Price = prices, 
  Availability = availability
)
```

```{r}
scraped |> glimpse()
```

```{r}
scraped |> knitr::kable()
```

## Data Wrangling and Viz

```{r}
df <- scraped |> 
  select(Title, Rating, Price) |> 
  mutate(Price = parse_number(Price),
         Rating = fct_relevel(Rating, 'One', 'Two', 'Three', 'Four', 'Five'))
df |> head(10)
```

```{r}
df |> 
  group_by(Rating) |> 
  summarise(Price = mean(Price)) |> 
  ggplot(aes(Rating, Price)) +
  geom_col(fill = '#99eeff') +
  theme_light()
```
